Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-12 response_to_reviewers.tex

\textbf{2. Response:}

\begin{quote}
\color{blue}
We have followed the reviewer's advise.
\end{quote}

\textbf{3. Reviewer's Comment:}

 Page 3, first paragraph of Data section in Materials \& Methods, final sentence: replace “correct for”
with “account for”.

@@

\textbf{3. Response:}

\begin{quote}
\color{blue}
We have followed the reviewer's advise.
\end{quote}

\textbf{4. Reviewer's Comment:}

Page 3, second paragraph of Data section in Materials \& Methods, first sentence: the two web
resources (Tree of Life Web Project and Global Butterfly Names project) should be listed in the
References section and treated as references in the manuscript (i.e. referred to by number).

@@

\begin{quote}
\color{blue}
We have removed the whole sentence as the reviewer recommended in point 5.
\end{quote}

\textbf{13. Reviewer's Comment:}
Page 6, sentence beginning “For the diversification shifts..”: the last phrase could use a verb; something like “when the MCC tree alone was used”.

\textbf{13. Response:}

\begin{quote}
\color{blue}
We added "was used" to the end of the sentence.
\end{quote}

\textbf{14. Reviewer's Comment:}
Page 6, sentence beginning “There were four...”: all shifts described are increases. If this is the case, the sentence can be simplified, moving the congruent part of each shift to a single instance preceding the list: “There were four net diversification rate increases found in the trees from the random sample (Table 2); the shifts occurred in: (i) the genus Ypthima (r = 0:22); (ii) the genus Charaxes (r = 0:21); (iii) Ithomiini subtribes Oleriina + Ithomiina + Napeogenina + Dircennina + Godyridina (r = 0:10); and (iv) the clade of Callicore + Diaethria (r = 0:135).”

\textbf{14. Response:}

\begin{quote}
\color{blue}
We modified the sentence as suggested by the reviewer.
\end{quote}

\end{document}

### 2015-01-12 MS_revised.tex
comment 14

There were four diversification shifts found in the trees from the
random sample (Table 2): (i) net diversification rate increase in the
genus \emph{Ypthima} (\(r = 0.22\)); (ii) net diversification rate
increase in the genus \emph{Charaxes} (\(r = 0.21\)); (iii) rate
increase in Ithomiini subtribes Oleriina + Ithomiina + Napeogenina +
Dircennina + Godyridina (\(r = 0.10\)); and (iv) rate increase in
\emph{Callicore} + \emph{Diaethria} (\(r = 0.135\)).

>>>>

There were four net diversification rate increases found in the trees from the
random sample (Table 2): (i) the
genus \emph{Ypthima} (\(r = 0.22\)); (ii) the genus \emph{Charaxes}
(\(r = 0.21\)); (iii) Ithomiini subtribes Oleriina + Ithomiina + Napeogenina +
Dircennina + Godyridina (\(r = 0.10\)); and (iv) the clade of 
\emph{Callicore} + \emph{Diaethria} (\(r = 0.135\)).
